---
title: "Introduction to FARS functions"
author: "Sandeep B M"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(FARSFunctions)
```

FARS is a nationwide census providing NHTSA, Congress and the American public yearly data regarding fatal injuries suffered in motor vehicle traffic crashes. This package provides a set of 5 functions that help to analyse FARS dataset:

- `fars_read()` to read CSV file and convert to tibble data frame
- `make_filename()` to construct file name using `year`
- `fars_read_years()` to consolidate fatalaties by month and year
- `fars_summarize_years()` to summarize fatalaties by month and year
- `fars_map_state()` to plot fatalities on map for gievn state and year


## Examples

Below code demonstrates examples of function usage:

```{r}
fars_read(make_filename(2015))
fars_read_years(c(2013,2014,2015))
fars_summarize_years(c(2013,2014,2015))
fars_map_state(1,2015)

```

